Missing data: Current practice in football research and recommendations for improvement

### 2020-09-10 paper/paper.Rmd
merge supplement 3.

---
title: "Missing data: Current practice in football research and recommendations for improvement"
authors: David N Borg(1,2), Robert Nguyen(3), Nicholas J Tierney(4,5)
output: 
  html_document:
    toc: true
    toc_float: true
    keep_md: true
bibliography: references.bib
---

@@

```{r libraries, message = FALSE}
library(tidyverse)
library(naniar)
library(visdat)
library(patchwork)
```

@@

2: Griffith University, School of Allied Health Sciences, Brisbane, Australia.

3: University of New South Wales, Department of Statistics, School of
Mathematics and Statistics, Sydney, Australia.

4: Monash University, Department of Econometrics and Business Statistics,
Melbourne, Australia.

5: Australian Centre of Excellence for Mathematical and Statistical
Frontiers (ACEMS), Melbourne, Australia.

@@

(Figure \@ref(fig:missing-overview)) give an overall sense of the extent of missing and complete data.

@@

# can

>>>>

---
title: "Missing data: Current practice in football research and recommendations for improvement"
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
output: 
  html_document:
    toc: true
    toc_float: true
    keep_md: true
bibliography: references.bib
---

@@

```{r libraries, message = FALSE}
library(tidyverse)
library(naniar)
library(visdat)
library(patchwork)
library(fitzRoy)
library(mice)
```

@@

2: University of New South Wales, Department of Statistics, School of
Mathematics and Statistics, Sydney, Australia.

3: Monash University, Department of Econometrics and Business Statistics,
Melbourne, Australia.

4: Australian Centre of Excellence for Mathematical and Statistical
Frontiers (ACEMS), Melbourne, Australia.

@@

(Figure \@ref(fig:missing-overview)) give an overall sense of the extent of missing and complete data. 
The simualted data set contains ... **Add short description (1-2 sentences) here of the simulated data set**

```{r}

# Aim of this section:
# Simulate data from a real data set, insert missing
# 'Study aim': predicting super coach scores

# Generate the x-variables
d <- get_afltables_stats(start_date = "2020-01-01", end_date = "2020-09-04")

data <-
  d %>% select(
    ID,
    Round,
    First.name,
    Surname,
    Kicks,
    Handballs,
    Marks,
    Hit.Outs,
    Contested.Possessions,
    Uncontested.Possessions
  )

```{r}

# Generate the y-variable
df <- get_footywire_stats(10286:10290) # Get the fantasy scores
fit <- lm(AF ~ K + HB, data = df)
summary(fit)
data %>% mutate(fanasty_score = 4.106*Kicks + 2.175*Handballs) # Need to work on this line

```{r}

# Put the dataset together
# Impute missing values
data <- ampute(data = df[,10:43])
data <- df_first_try$amp

@@
